Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-21 talk/pepm2011/paper.tex
fix some of anto's issues, will try to add line numbers now

The main insight to improve the code shown in section \ref{sub:example} is that objects
in category 1 do not survive very long -- they are used only inside the loop and
there is no other outside reference to them. The optimizer identifies objects in
category 1 and removes the allocation of these objects, and all operations
manipulating them.

@@

The following operations (lines 10-17) are more interesting:
\anto{what about putting the line numbers also here? Moreover, figure 4 is put just after this listing, it could be confused}

@@

\anto{I don't like ``how the object looks like''. I don't know what else to say, though :-(} 
When the optimizer encounters a \lstinline{new}, it removes it optimistically,
and assumes that the object is in category 1. If later the optimizer finds that the object escapes, it
will be allocated at that point. The optimizer needs to keep track
of how the object that the operation creates looks like at various points in
the trace. This is done with the help of a \emph{static object}\footnote{Here
``static'' is meant in the sense of partial evaluation, \ie known at partial
evaluation time, not in the sense of ``static allocation'' or ``static
method''.}. The static object describes the shape of the object that would have
been allocated, \ie the type of the object and where the values that would be
stored in the fields of the allocated object come from.

>>>>

The main insight to improve the code shown in Section~\ref{sub:example} is that objects
in category 1 do not survive very long -- they are used only inside the loop and
there is no other outside reference to them. The optimizer identifies objects in
category 1 and removes the allocation of these objects, and all operations
manipulating them.

@@

The following operations (lines 10-17) are more interesting:
% XXX line numbers

@@

When the optimizer encounters a \lstinline{new}, it removes it optimistically,
and assumes that the object is in category 1. If later the optimizer finds that the object escapes, it
will be allocated at that point. The optimizer needs to keep track
of the state of the object that the operation would have created.
This is done with the help of a \emph{static object}\footnote{Here
``static'' is meant in the sense of partial evaluation, \ie known at partial
evaluation time, not in the sense of ``static allocation'' or ``static
method''.}. The static object describes the shape of the object that would have
been allocated, \ie the type of the object and where the values that would be
stored in the fields of the allocated object come from.
